\documentclass{article}

\usepackage{titlesec}
\usepackage{titling}
\usepackage[margin=0.5in]{geometry}
\usepackage{enumitem}

\titleformat{\section}
{\large\bfseries}
{}
{0em}
{}[\titlerule]


\titleformat{\subsection}[runin]
{\bfseries\large}
{}
{0em}
{}

\titleformat{\subsubsection}
{\itshape}
{}
{0em}
{}

\titlespacing{\subsection}
{0em}{0em}{0.5 em}

\titlespacing{\subsubsection}
{0em}{0em}{0.9em}


\renewcommand{\maketitle}{

\begin{center}
{\huge\bfseries
\thetitle}

\vspace*{0.5cm}

swapnil@hku.hk | +852 6991 8015 | https://hiswapnil.me | +358 40 252 8029 | https://github.com/hiswaps

\end{center}
}


\begin{document}

\title{SWAPNIL JOSHI}
%\author{Swapnil Joshi}
\maketitle
\thispagestyle{empty} 

%{\href{https://www.github.com/hiswaps}{GitHub Profile}| \href{https://www.linkedin.com/in/joshisj}{LinkedIn Profile}\\
%{swapnil@hku.hk} | +358 40 252 8029 | +852 6991 8015 | \href{mailto:hk.swaps@gmail.com}{hk.swaps@gmail.com}



%Education

\section{EDUCATION}
\vspace{-1.5mm}
\subsection{The University of Hong Kong \hspace{4.12in} Hong Kong}
\subsubsection{Bachelor of Engineering in Computer Science; Self-declared Minor in Finance \hspace{1.29in} Sep. 2017 - Jun. 2021}
\vspace{-2.9mm}
\begin{itemize}[noitemsep]
%\item \textbf{Coursework:} Data Structures and Algorithms, Programming Technologies and Tools, Discrete Mathematics 
\item  \textbf{External Events:} J.P. Morgan Early Advantage Program; J.P. Morgan Trading Game Challenge; Amplify Trading S\&T Workshop; S\&T Competition at Asia Investment \& Banking Conference; 

\end{itemize}

\vspace{-1.6mm}

\subsection{Aalto University \hspace{4.8in} Espoo, Finland}
\subsubsection{Exchange —  Computer, Communication, and Information Science \hspace{2.1in} Jan. 2020 - May 2020}
\vspace{-2.9mm}
\begin{itemize}[noitemsep]
\item \textbf{Relevant Coursework:} Software Engineering, Advanced Mathematical Algorithms, Artificial Intelligence, Data Visualization
\end{itemize}

\vspace{-7.1mm}
%Personal Trading

\section{PERSONAL TRADING EXPERIENCE}
\vspace{-2mm}
\begin{itemize}[noitemsep]
%\setlist{topsep=0pt}

\item Self-taught the nuances of options theory (volatility and trading) and managed a US\$67,000 portfolio.
\item Developed uncorrelated option trading strategies on U.S. equities, ETFs (XOP, USO, GDX, SLV, SPY, QQQ, VVX), and crude oil futures — to diversify risk and generate high returns.
\item Currently working towards development of a trading model using Machine Learning techniques.
\end{itemize}

\vspace{-6.5mm}

%Work Experience

\section{WORK EXPERIENCE}
\vspace{-2mm}
\subsection{Nomisma Holdings Pte. Ltd. \hspace{4.1in} Hong Kong}
\subsubsection{Summer Research Intern \hspace{4.5in} Aug. 2019 - Sep. 2019}
\vspace{-2.9mm}
\begin{itemize}[noitemsep]
\item Worked closely with the quant team to assist with the prototyping of trading matching engine for our exchange, which
resulted in \textbf{faster completion of the task by 7 days}.
\item Developed research templates to perform top-down competitor analysis, \textbf{resulting in 2x productivity}.
\end{itemize}

\vspace{-1.6mm}

\subsection{trade.io \hspace{5.85in} Hong Kong}
\subsubsection{Blockchain Research Analyst \hspace{4.3in} Sep. 2018 - Dec. 2018}
\vspace{-2.9mm}
\begin{itemize}[noitemsep]
\item Conducted blockchain market research and created pitch books for clients in Latin America.
\item Made recommendations on ideal blockchain platform for clients to build their decentralized apps.
\item Created ICO security pitch decks and assisted the marketing team in building materials for investors.
\end{itemize}

\vspace{-1.6mm}

\subsection{Independent Trader and Asset Manager \hspace{3.3in} Hong Kong}
\subsubsection{Research and Portfolio Management Intern \hspace{3.5in} Jun. 2018 - Dec. 2018}
\vspace{-2.9mm}
\begin{itemize}[noitemsep]
\item Monitored client portfolios, reported daily P/L, and made recommendations on potential stock investments. Later
allocated capital to selected stocks and delivered an \textbf{absolute return of 12.84\% in 3 months}.
\item Implemented the DCF analysis and found that a pharmaceutical firm’s stock was undervalued 10-11\% due to sector
slowdown, and global trade tensions.
\item Recommended investing based on long-term earnings growth, and firm’s strong corporate governance. Stock later
\textbf{appreciated 17\% in 2 months}.
\end{itemize}


%Portfolio
\vspace{-6mm}
\section{PROJECTS}
\vspace{-3mm}
\subsection{pytops (2020)} -- Developed and published an open-source Python package -- \textbf{pytops}, for quick and simple pricing of options using the \textbf{Black-Scholes pricing model}, and to compute the option greeks. The package has been built using Python 3.6 and has minimum dependencies on external libraries. The functions have been implemented efficiently using the scientific computation libraries -- \textbf{numpy}, and \textbf{scipy}.
%\begin{itemize}[noitemsep]
%\item Developed and published an open-source Python package -- \textbf{pytops}, for quick and simple pricing of options using the \textbf{Black-Scholes pricing model}.
%\item 
%\end{itemize}

\vspace{-2.5mm}



\section{EXTRACURRICULAR ACTIVITIES}
\vspace{-1.5mm}

\subsection{TEDxHKU 2018: MOTION \hspace{4.2in} Hong Kong}
\subsubsection{Organizer \hspace{5.5in} Feb. 2018 - Nov. 2018}
\vspace{-2.9mm}
\begin{itemize}[noitemsep]
\item \textbf{Led a team of 30 students}; directed the operations \& management of the \textbf{most successful TEDxHKU till date}.
\item Liaised with different departments within HKU and helped \textbf{secure sponsorships for the event}.
\end{itemize}

%Skills

\section{SKILLS \& INTERESTS}
\vspace{-2mm}
\begin{itemize}[noitemsep]
\item \textbf{Programming:} Python, JavaScript, HTML, CSS, C++
\item \textbf{Tools \& Technologies:} Git, {\LaTeX}, MS Word, MS PowerPoint, Visual Basic, T.R. Eikon, S\&P Capital IQ
\item \textbf{Libraries \& Frameworks:} React, Node.js, AngularJS
\item \textbf{Interests:} Horserace Betting, Formula-1 Racing, Rowing, Music Production - Hip Hop \& EDM, Guitar, Moutaineering
\end{itemize}


\end{document}

